An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-06-08 poly-embed-journal/poly-embed-journal.tex
minor

  For the converse, suppose $L$ has a polyhedral Bayes risk, which implies it has a finite minimum representative set, we construct the set $\Sc$ as follows:
  since the epigraph of negative Bayes risk $E_L$ is polyhedral, it has finitely many facets, and we iterate over these.
  Each facet $F$ of $E_L$ must be full dimensional by definition of a facet, and therefore there must be some $p \in \inter{F}$.
  Observe that $p$ must by uniquely supported by some hyperplane $p \mapsto (p, L(u))$ for some $u \in \R$, since it is in the interior of the facet (and therefore $\risk{L}$ is differentiable at $p$).
  Add $u$ to $\Sc$, and repeat, iterating over each of $E_L$'s finitely many facets.
  We now show $\Sc$ is a minimum representative set.

@@

\begin{definition}\label{def:power-diagram}
  Given sites $s_1,\ldots,s_k\in\reals^d$ and weights $w_1,\ldots,w_k \geq 0$, the corresponding \emph{power diagram} is the cell complex given by
  \begin{equation}
    \label{eq:pd}
    \cell(s_i) = \{ x \in\reals^d : \forall j \in \{1,\ldots,k\} \, \|x - s_i\|^2 - w_i \leq \|x - s_j\| - w_j\}~.
  \end{equation}
\end{definition}

>>>>

  For the converse, suppose $L$ has a polyhedral Bayes risk $\risk{L}$.
  Then we may write $\risk{L}(p) = \min_{(a,b)}$

  Let $\F$ be the set of facets of the epigraph of the negative Bayes risk

  implies it has a finite minimum representative set, we construct the set $\Sc$ as follows:

  since the epigraph of negative Bayes risk $E_L$ is polyhedral, it has finitely many facets, and we iterate over these.
  Each facet $F$ of $E_L$ must be full dimensional by definition of a facet, and therefore there must be some $p \in \inter{F}$.
  Observe that $p$ must by uniquely supported by some hyperplane $p \mapsto (p, L(u))$ for some $u \in \R$, since it is in the interior of the facet (and therefore $\risk{L}$ is differentiable at $p$).
  Add $u$ to $\Sc$, and repeat, iterating over each of $E_L$'s finitely many facets.
  We now show $\Sc$ is a minimum representative set.

@@

\begin{definition}\label{def:power-diagram}
  Given sites $s_1,\ldots,s_k\in\reals^d$ and weights $w_1,\ldots,w_k \geq 0$, the corresponding \emph{power diagram} is the cell complex given by
  \begin{equation}
    \label{eq:pd}
    \cell(s_i) = \{ x \in\reals^d : \forall j \in \{1,\ldots,k\} \, \|x - s_i\|^2 - w_i \leq \|x - s_j\|^2 - w_j\}~.
  \end{equation}
\end{definition}
